Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2023-08-16 2_SSL_NE/article/article_main.tex
updated figures

\begin{figure}[h!]
 \centering
 \includegraphics[width=\textwidth]{figures/breakthroughs_efficiency.pdf}
 \caption{\textbf{Contribution of innovations and technology spillovers to the historical progress in sub-efficiencies of phosphor-converted warm white LEDs.} LEDs with test currents of at least 350mA are considered. The following sub-efficiencies are represented: $\eta_{V_f}$ - forward voltage efficiency; $\eta_IQ$ - internal quantum efficiency; $η_{droop}$ - efficiency droop; $\eta_{LE}$ - light extraction efficiency; $\eta_{C_R}$ - conversion efficiency for red phosphors; $\eta_{C_{Y/G}}$ - conversion efficiency for yellow/green phosphors; $\eta_S$ - spectral efficiency. The overall LED lamp efficiency $\eta_L$ is displayed in the rightmost column. Vertical bars represent cumulative contributions to efficiency improvements from LED technology innovations, with purple bars indicating innovations driven by technology spillovers (annotated and listed in an inset table) and grey bars indicating all other improvements identified in this study. Horizontal coloured lines indicate sub-efficiency levels of best performing LEDs for the four years used in \cref{fgr:waterfall}: 2003, 2010, 2016, and 2020. For additional historical context, data for 1997 is included whenever possible. "N/A" denotes sub-efficiencies where 1997 data could not be calculated for the following reasons: $\eta_{V_f}, \eta_{droop}$ depend on the device current, which was below 350mA in 1997, making a comparison with contemporary devices difficult. $\eta_{C_R}, \eta_{C_{Y/G}}$ and $\eta_S$ are relevant only to warm white spectrum LEDs, which were not available in 1997. Note: ITO current spreading layer affects different sub-efficiencies in different chip architectures, e.g., in modern flip-chip architectures $\eta_{LE}$ no longer depends on ITO, see \cref{fgr:chip_architecture_overview}. Physical limits on sub-efficiencies are indicated by black horizontal lines. Note that the physical limit of $\eta_{V_f}$ is above 100\% due to quantum effects \cite{david2016electrical}. Source: own elaboration based on data represented in \cref{fgr:waterfall}, \cref{tab:spillovers} and Supplementary Note 4.}
 \label{fgr:breakthroughs_efficiency}
\end{figure}

@@

\begin{figure*}[h!]
 \centering
 \includegraphics[width=17.5cm]{figures/costmodel_results_years.pdf}
 \caption{Manufacturing cost structure modelled for a single low-to-mid power GaN, classic chip, phosphor-converted white LED package, assuming an ideal factory with state-of-the-art equipment at a U.S. location. Consecutive steps shown on the x-axis. Panels A-C: Waterfall diagrams of LED manufacturing cost split by manufacturing process steps for years 2003, 2012 and 2020. Process steps on the horizontal axis are sequenced from left to right in the same order as in the modelled LED manufacturing process. Panel F: Cumulative manufacturing yield after each process step for years 2003, 2012 and 2020. For a visual representation of the overview of the manufacturing process, compare the diagrams in Section 2 of the Supplementary Information. Abbreviations: Litho – Lithographic Process, Insp. – Inspection, Depn. – Deposition, CMP - Chemical-Mechanical Planarization}
 \label{fgr:costmodel}
\end{figure*}

>>>>

\begin{figure}[h!]
 \centering
 \includegraphics[width=\textwidth]{figures/breakthroughs_efficiency.pdf}
 \caption{\textbf{Contribution of innovations and technology spillovers to the historical progress in sub-efficiencies of phosphor-converted warm white LEDs.} LEDs with test currents of at least 350mA are considered. The following sub-efficiencies are represented: $\eta_{V_f}$ - forward voltage efficiency; $\eta_IQ$ - internal quantum efficiency; $\eta_{droop}$ - efficiency droop; $\eta_{LE}$ - light extraction efficiency; $\eta_{C_R}$ - conversion efficiency for red phosphors; $\eta_{C_{Y/G}}$ - conversion efficiency for yellow/green phosphors; $\eta_S$ - spectral efficiency. The overall LED lamp efficiency $\eta_L$ is displayed in the rightmost column. Vertical bars represent cumulative contributions to efficiency improvements from LED technology innovations, with purple bars indicating innovations driven by technology spillovers (annotated and listed in an inset table) and grey bars indicating all other improvements identified in this study. Horizontal coloured lines indicate sub-efficiency levels of best performing LEDs for the four years used in \cref{fgr:waterfall}: 2003, 2010, 2016, and 2020. For additional historical context, data for 1997 is included whenever possible. "N/A" denotes sub-efficiencies where 1997 data could not be calculated for the following reasons: $\eta_{V_f}, \eta_{droop}$ depend on the device current, which was below 350mA in 1997, making a comparison with contemporary devices difficult. $\eta_{C_R}, \eta_{C_{Y/G}}$ and $\eta_S$ are relevant only to warm white spectrum LEDs, which were not available in 1997. Note: ITO current spreading layer affects different sub-efficiencies in different chip architectures, e.g., in modern flip-chip architectures $\eta_{LE}$ no longer depends on ITO, see \cref{fgr:chip_architecture_overview}. Physical limits on sub-efficiencies are indicated by black horizontal lines. Note that the physical limit of $\eta_{V_f}$ is above 100\% due to quantum effects \cite{david2016electrical}. Source: own elaboration based on data represented in \cref{fgr:waterfall}, \cref{tab:spillovers} and Supplementary Note 4.}
 \label{fgr:breakthroughs_efficiency}
\end{figure}

@@

\begin{figure*}[h!]
 \centering
 \includegraphics[width=17.5cm]{figures/costmodel_results_years.pdf}
 \caption{\textbf{Historical changes in LED manufacturing cost structure.} Presented cost calculations are an outcome of our cost model (see \cref{sec:methods} and \cref{costmodel_details}) for a single low-to-mid power GaN-based, classic chip, phosphor-converted white LED package, assuming an ideal factory with state-of-the-art equipment at a U.S. location. Panels A-C: Waterfall diagrams of LED manufacturing cost structure split by manufacturing process steps for years 2003, 2012 and 2020. Process steps on the horizontal axis are sequenced from left to right in the same order as in the modelled LED manufacturing process. Panel D: Cumulative manufacturing yield after each process step for years 2003, 2012 and 2020. For a graphic representation of the manufacturing process, see the diagrams in \cref{subsec:manufacturing_steps}. Abbreviations: Litho – Lithographic Process, Insp. – Inspection, Depn. – Deposition, CMP - Chemical-Mechanical Planarization.}
 \label{fgr:costmodel}
\end{figure*}

### 2023-08-16 2_SSL_NE/article/article_supplementary.tex
added edits
updated figures

% nature energy custom code

\newcounter{supplementarynote}
\renewcommand{\thesupplementarynote}{\arabic{supplementarynote}}
\newcommand{\supplementarynote}{%
  \refstepcounter{supplementarynote}%
  Supplementary Note~\thesupplementarynote:~%
}
\titleformat{\section}
  {\normalfont\large\bfseries}
  {\supplementarynote}
  {0em} % Adjust this value to control the spacing
  {}
\renewcommand{\thesection}{\thesupplementarynote}

@@

Light conversion efficiency (LCE) describes the losses in the conversion process of blue light that is the basis for all phosphor-converted white LEDs. These losses are the sum of the Stokes loss and  scattering/absorption losses. It is defined as
%
\begin{equation}
    \eta_{C} = \frac{E_{\textcolor{blue}{B}}}{\sum_{i=\textcolor{red}{R},\textcolor{orange}{O},\textcolor{yellow}{Y},\textcolor{teal}{G}} E_i}
\end{equation}
%
where $E_i$ denotes the total energy of light at the color $i$ corresponding to the down-converted photon wavelength \cite{schubert2018light}\cite{tsao2010solid}. Since every individual phosphor component in the device has its own associated conversion losses, the denominator sums over all phosphor components, i.e. \textcolor{red}{R}ed, \textcolor{orange}{O}range, \textcolor{yellow}{Y}ellow, \textcolor{teal}{G}reen.

@@

\subsubsection{Manufacturing Process Steps by Chip Architecture}

>>>>

% nature energy custom code
\makeatletter
\renewcommand{\@seccntformat}[1]{Supplementary Note \csname the#1\endcsname\quad}
\makeatother

@@

Light conversion efficiency (LCE) describes the sum of all losses in the process of converting the blue light that is the basis for all phosphor-converted white LEDs. Specifically, energy is lost due to three distinct effects. First, the inherent wavelength-conversion loss or \textit{Stokes shift} as the difference between the original blue wavelength and the down-converted red, yellow or green wavelength. Second, non-radiative processes in the phosphor material. Third, scattering and absorption processes in the phosphor material. These three effects are listed individually in \cref{fgr:waterfall}. The overall light conversion efficiency is defined as
%
\begin{equation}
    \eta_{C} = \frac{E_{\textcolor{blue}{B}}}{\sum_{i=\textcolor{red}{R},\textcolor{orange}{O},\textcolor{yellow}{Y},\textcolor{teal}{G}} E_i}
\end{equation}
%
where $E_i$ denotes the total energy of light at color $i$ corresponding to the down-converted photon wavelength \cite{schubert2018light}\cite{tsao2010solid}. Since every individual phosphor component in the device has its own associated conversion losses, the denominator sums over all phosphor components, i.e. \textcolor{red}{R}ed, \textcolor{orange}{O}range, \textcolor{yellow}{Y}ellow, \textcolor{teal}{G}reen.

@@

\subsubsection{Manufacturing Process Steps by Chip Architecture}
\label{subsec:manufacturing_steps}
